Perturbed Gait Data

### 2014-10-21 paper.tex
added figures if needed
Simulink diagram, comparison of input and output of perturbation signals

\section{Perturbation Signals}
%
The data set uses a testing protocol containing a segment of normal walking,
followed by a series of pseudo-random longitudinal perturbations, and ending
with a second segment of normal walking. Three pseudo-random speed control
signals, with mean velocities of 0.8, 1.2, and 1.6 $m \cdot s^{-1}$, were
generated through MATLAB and Simulink. Initially, a random acceleration signal
was created using discrete-time Gaussian white noise and saturated at the
maximum belt acceleration of 15 $m \cdot s^{-2}$, integrated to obtain belt
speed, and high-pass filtered (second-order Butterworth) to eliminate velocity
drift. Mean velocity was then added to the signal and limited between 0 and 3.6
m/s. The cutoff frequencies of the high-pass filter, as well as the variance in
the acceleration signal, were adjusted until the appropriate standard
deviations for each mean velocity were obtained.

@@

The resulting output from the MATLAB script and Simulink produces a comma-
delimited text file of six columns: timestamp, slow, normal, and fast walking
perturbation signals, and slow and fast running signals.  These running signals
were generated in the event the testing protocol expanded from a walking study
to a running study, though they were not used in the data set.

>>>>

\section{Perturbation Signals}
%
The data set uses a testing protocol containing a segment of normal walking,
followed by a series of pseudo-random longitudinal perturbations, and ending
with a second segment of normal walking. Three pseudo-random speed control
signals, with mean velocities of 0.8, 1.2, and 1.6 $m \cdot s^{-1}$, were
generated through MATLAB and Simulink (Figure~\ref{fig:simulink}). Initially, a 
random acceleration signal was created using discrete-time Gaussian white 
noise and saturated at the maximum belt acceleration of 15 $m \cdot s^{-2}$,
integrated to obtain belt speed, and high-pass filtered (second-order
Butterworth) to eliminate velocity drift. Mean velocity was then added to the 
signal and limited between 0 and 3.6 m/s. The cutoff frequencies of the high-
pass filter, as well as the variance in the acceleration signal, were adjusted 
until the appropriate standard deviations for each mean velocity were obtained.

\begin{figure}
  \includegraphics{figures/longitudinal_perturbation.PNG}
  \caption{MATLAB Simulink model for generating longitudinal perturbations,
                given variance, cutoff frequency of the high-pass filter, and
                the average speed}
  \label{fig:simulink}
\end{figure}

@@

The resulting output from the MATLAB script and Simulink produces a comma-
delimited text file of six columns: timestamp, slow, normal, and fast walking
perturbation signals, and slow and fast running signals.  These running signals
were generated in the event the testing protocol expanded from a walking study
to a running study, though they were not used in the data set.  The actual motion
of the treadmill belts are compared to the original input signals, shown in 
Figure~\ref{fig:input_output}.

\begin{figure}
  \includegraphics{figures/input_vs_output.eps}
  \caption{Generated input signal (black) and actual treadmill belt movement
                (red) for average speeds of 0.8, 1.2, and 1.6 m/s, respectively}
  \label{fig:input_output}
\end{figure}
